intro

### 2022-03-10 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update Hypotheses 4
comment on Hyp. 4, reformulated Hyp. 4

* H4a) Subjective effort ratings negatively predict SVs of ER strategies.
* H4b) Subjective arousal ratings negatively predict SVs of ER strategies.
* H4c) EMG *corrugator* activity negatively predicts SVs of ER strategies.
* H4d) EMG *levator* activity negatively predicts SVs of ER strategies.
* H5a) SVs decline with increasing effort, even after controlling for task performance measured by subjective arousal ratings, *corrugator* and *levator* activity.

>>>>

* H4a) Subjective effort negatively predicts SVs of ER strategies.
* H4b) Subjective arousal negatively predicts SVs of ER strategies.
* H4c) Physiological arousal / valence (EMG *corrugator* activity) negatively predicts SVs of ER strategies.
* H4d) Physiological arousal / valence (EMG *levator* activity) negatively predicts SVs of ER strategies.

<!-- Denise: Für Hyp. 4 kann ich leider ganz schlecht beurteilen, ob eure stat. Analyse diese Hyp. beantwortet, da ich die stat. Analyse noch nicht so richtig verstanden habe -->

* H5a) SVs decline with increasing effort, even after controlling for task performance measured by subjective arousal ratings, *corrugator* and *levator* activity.
